\chapter{Prometheus}
We use Prometheus to access the K8s clusters metrics. To avoid a self-writing manifest we copied some from an existing demonstration project which is called \href{https://github.com/microservices-demo/microservices-demo}{Socket Shop}.

\section{On local K8s cluster}
To test our environment and start developing the application we need to set up our local Kubernetes cluster with the Prometheus monitoring interface. This interface can be configured locally with some cluster configuration files. For this case, there is the folder "manifests-monitoring". Our application should run on the local Kubernetes cluster and this application should be able to monitor a K8s cluster. In our environment, we decided to monitor our local cluster, where also our application is running on.

With the configuration files in the "kubernetes-manifests" folder, we can deploy this cluster. The configuration files in the "manifests-monitoring" folder install and set up the Prometheus environment which is monitored automatically our cluster.

\section{Installation of Prometheus}
To start the Prometheus monitoring you can just start minikube first from your console and then start the web application directly from WebStorm. The setup is configured in a way so that you only need to start the web application in the cluster. Then, Prometheus monitoring will automatically start for you. Remember to stop the minikube service when you finish your development session. On the WebStorm console, there will be all the IP addresses and the Ports list which you need to use to access Prometheus or our local web application.

For detailed and up-to-date instructions, please see our repository\footnote{\url{https://gitlab.ost.ch/SEProj/2022-FS/g03-kubewatch/kubewatch}}.


% \section{On INS K8s cluster}